---
title: "R Notebook"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

This notebook demos opening different Excel files and printing their output.
```{r}
library(readxl)
library(data.table)
library(ggplot2)
library(signal)

library(dplyr)
library(stringr)
library(directlabels)

library(knitr)
library(kableExtra)
library(latex2exp)

source("utils.R")
output_dir <- "../../../output/"
```

Now--great--can we compare different sheets?

```{r}

#source_path <- "../data/multirun_n100_eeba_rolf/"
#source_path <- "../data/multirun_n100_eeba_rolf_attempt2/"
#comparison_folder <- "multirun_n100_eeba_rolf"
comparison_folder <- "multirun_n100_reward_to_util_transform"
source_path <- paste0("/Volumes/SeagateTimeMachine/workspace/morl_project_data/morlglue-clients-data/",comparison_folder,"/")
start_time <- Sys.time()

#file_list <- get_csv_file_list(source_path)

#raw_activity <- get_raw_csv_activity_dt(file_list[1:5,],source_path)
raw_activity <- get_presummarized_csv_activity_dt(source_path)

episode_summary<-raw_activity$episode_summary
run_summary<-raw_activity$run_summary
print(object.size(raw_activity))

#get memory efficiencies
# raw_activity$EpisodeType <- as.factor(raw_activity$EpisodeType)
# raw_activity$Environment <- as.factor(raw_activity$Environment)
# raw_activity$Agent <- as.factor(raw_activity$Agent)
# 
# #it's pretty big; this will make operations more efficient.
# raw_activity <- data.table(raw_activity)


end_time <- Sys.time()
duration <- end_time - start_time
print(duration)



```


```{r}

print(object.size(episode_summary))

print(object.size(run_summary))
```



About 10% faster. Not sure this is significant but whatever.


Filter out SFMLA because it hasn't performed well and there's no point including it.


## Additional data labelling

```{r}

environment_labels <- str_match(episode_summary$Environment,"(pen|rew)(\\d+.?\\d*)")
episode_summary$EnvironmentVariant <- environment_labels[,1]
episode_summary$EnvironmentDimChange <- environment_labels[,2]
episode_summary$EnvironmentValueChange <- as.numeric(environment_labels[,3])
episode_summary[is.na(episode_summary$EnvironmentVariant),]$EnvironmentVariant <- "Base"
episode_summary[is.na(episode_summary$EnvironmentDimChange),]$EnvironmentDimChange <- ""
episode_summary$ObjectiveDimChange=""
episode_summary[EnvironmentDimChange=="pen",ObjectiveDimChange:="Alignment"]
episode_summary[EnvironmentDimChange=="rew",ObjectiveDimChange:="Performance"]

environment_labels <- str_match(run_summary$Environment,"(pen|rew)(\\d+.?\\d*)")
run_summary$EnvironmentVariant <- environment_labels[,1]
run_summary$EnvironmentDimChange <- environment_labels[,2]
run_summary$EnvironmentValueChange <- as.numeric(environment_labels[,3])
run_summary[is.na(run_summary$EnvironmentVariant),]$EnvironmentVariant <- "Base"
run_summary[is.na(run_summary$EnvironmentDimChange),]$EnvironmentDimChange <- ""
run_summary[is.na(run_summary$EnvironmentValueChange),]$EnvironmentValueChange <- 1
run_summary$ObjectiveDimChange=""
run_summary[EnvironmentDimChange=="pen",ObjectiveDimChange:="Alignment"]
run_summary[EnvironmentDimChange=="rew",ObjectiveDimChange:="Performance"]
```

Convert applicable columns to factors. Important because they will use up less space than strings.


```{r}
episode_summary$EnvironmentClass <- as.factor(episode_summary$EnvironmentClass)
episode_summary$EnvironmentVariant <- as.factor(episode_summary$EnvironmentVariant)
episode_summary$EnvironmentDimChange <- as.factor(episode_summary$EnvironmentDimChange)
episode_summary$ObjectiveDimChange <- as.factor(episode_summary$ObjectiveDimChange)
episode_summary$Agent <- as.factor(episode_summary$Agent)
episode_summary$Environment <- as.factor(episode_summary$Environment)
episode_summary$EpisodeType <- as.factor(episode_summary$EpisodeType)

run_summary$EnvironmentClass <- as.factor(run_summary$EnvironmentClass)
run_summary$EnvironmentVariant <- as.factor(run_summary$EnvironmentVariant)
run_summary$EnvironmentDimChange <- as.factor(run_summary$EnvironmentDimChange)
run_summary$ObjectiveDimChange <- as.factor(run_summary$ObjectiveDimChange)
run_summary$Agent <- as.factor(run_summary$Agent)
run_summary$Environment <- as.factor(run_summary$Environment)
run_summary$EpisodeType <- as.factor(run_summary$EpisodeType)

print(object.size(episode_summary))
```




```{r}
sapply(episode_summary,class)

```

We should have run IDs but no need for file IDs.

```{r}
#unneed to give runIDs as these are now already there.

#raw_activity_unique_runs <- raw_activity[,.(Agent,Environment,EnvironmentClass,FileID)] %>% unique()

#then give unique Run IDs, not file IDs
#raw_activity_unique_runs[,RunId:=1:.N,.(Agent,Environment,EnvironmentClass)]
#raw_activity <- merge(raw_activity,raw_activity_unique_runs)
#raw_activity$FileID<-NULL

rm(environment_labels)

```


## Postprocessing


## Offline performance

```{r}
table_env <- data.table(run_summary)[EpisodeType=="Offline",]
table_env$EpisodeType=NULL
#table_env$Environment=NULL
table_env$`Episode number`=NULL
table_env$`R^P`=NULL
table_env$`R^A`=NULL

table_env_long <- table_env %>% dcast.data.table(Environment~Agent,value.var="R^*",fun.aggregate = mean)
print(knitr::kable(table_env_long))


```




```{r}
table_env <- data.table(run_summary)[EpisodeType=="Online",]
table_env$EpisodeType=NULL
#table_env$Environment=NULL

table_env$`R^P`=NULL
table_env$`R^A`=NULL

table_numeric_vals <- table_env %>% dcast.data.table(
  EnvironmentClass+ObjectiveDimChange+EnvironmentValueChange~Agent
  ,value.var="R^*",fun.aggregate = mean)
```

```{r}
table_env_run_means <- table_env[,
          c(mean(`R^*`))
          
          ,by=.(Agent,Environment,EnvironmentClass,RunId,EnvironmentVariant,EnvironmentDimChange,EnvironmentValueChange,ObjectiveDimChange)]

setnames(table_env_run_means,"V1","Run_Mean_R^*")

#ctrl_agent<-"TLO_A"
ctrl_agent<-"LIN_SUM"

control_run_means <- table_env_run_means[Agent==ctrl_agent]
control_run_means$Agent=NULL
exp_run_means <- table_env_run_means[Agent!=ctrl_agent]

run_means_agent_comparison <- merge(
  control_run_means,exp_run_means,by =setdiff(colnames(exp_run_means),c("Run_Mean_R^*","Agent")),
  suffixes = c("_control","_experimental"))
exp_summary_stats <- run_means_agent_comparison[
  ,.(`Trial_Mean_R^*`=mean(`Run_Mean_R^*_experimental`),
    `Trial_SD_R^*`=sd(`Run_Mean_R^*_experimental`),
    `Trial_Mean_R^*_diff_pvalue`=t.test(`Run_Mean_R^*_control`,`Run_Mean_R^*_experimental`)$p.value,
    `Trial_Mean_R^*_diff_ci95_lower`=t.test(`Run_Mean_R^*_control`,`Run_Mean_R^*_experimental`)$conf.int[[1]],
    `Trial_Mean_R^*_diff_ci95_upper`=t.test(`Run_Mean_R^*_control`,`Run_Mean_R^*_experimental`)$conf.int[[2]]
    )
  ,by=.(Agent,Environment,EnvironmentClass,EnvironmentVariant,EnvironmentDimChange,EnvironmentValueChange,ObjectiveDimChange)]
                                               

get_formatted_desc <- function(x,pval){
  paste0(formatC(x,digits=2,format="f"),ifelse(pval<0.05,"*",""),ifelse(pval<0.01,"*",""),ifelse(pval<0.001,"*",""))
}
# exp_summary_stats[,exp_desc:=paste0(formatC(`Trial_Mean_R^*`,digits=2,format="f"),ifelse(`Trial_Mean_R^*_diff_pvalue`<0.05,"*",""),ifelse(`Trial_Mean_R^*_diff_pvalue`<0.01,"*",""),ifelse(`Trial_Mean_R^*_diff_pvalue`<0.001,"*",""))]
exp_summary_stats[,exp_desc:=get_formatted_desc(`Trial_Mean_R^*`,`Trial_Mean_R^*_diff_pvalue`)]

control_summary_stats <- control_run_means[
  ,
  .(TLO_A=get_formatted_desc(mean(`Run_Mean_R^*`),1)),
  by=.(EnvironmentClass,ObjectiveDimChange,EnvironmentValueChange)]


summary_stats_wide <- exp_summary_stats %>% dcast.data.table(
  EnvironmentClass+ObjectiveDimChange+EnvironmentValueChange~Agent,value.var="exp_desc") %>%
  merge(control_summary_stats)
```


```{r, knit}
table_env_long <- summary_stats_wide
#change this column name.
colnames(table_env_long) <- stringr::str_replace(colnames(table_env_long),"TLO_A","TLO$^A$")
setnames(table_env_long,"EnvironmentClass","Environment",skip_absent=TRUE)
setnames(table_env_long,"EnvironmentValueChange","Objective Scale",skip_absent=TRUE)
setnames(table_env_long,"ObjectiveDimChange","Objective Modified",skip_absent=TRUE)
setnames(table_env_long,"SFLLA","SFELLA",skip_absent=TRUE)

#colnames(table_env_long) <- stringr::str_replace(colnames(table_env_long),"Envir","$TLO^A$")
table_env_long <- 
  table_env_long %>% 
  mutate(Environment=str_replace(Environment,"BreakableBottles","Breakable Bottles")) %>%
  mutate(Environment=str_replace(Environment,"UnbreakableBottles","Unbreakable Bottles"))
  
#highlight results within 10% of the best value in each row.
row_max <- apply(table_numeric_vals[,4:ncol(table_numeric_vals)],1,max)*0.9<table_numeric_vals[,4:ncol(table_numeric_vals)]

table_env_long %>%
  mutate(`Objective Scale`=format(`Objective Scale`,scientific = FALSE,drop0trailing = TRUE)) %>%
  #mutate_if(is.numeric,~formatC(.x,digits=2,format="f"),"latex") %>%
  #mutate(LELA=cell_spec(LELA,"latex",color=ifelse(row_max[,'LELA'],"blue","black"))) %>%
  #mutate(SFELLA=cell_spec(SFELLA,"latex",color=ifelse(row_max[,'SFLLA'],"blue","black"))) %>%
  #mutate(ELA=cell_spec(ELA,"latex",color=ifelse(row_max[,'ELA'],"blue","black"))) %>%
  #mutate(SEBA=cell_spec(SEBA,"latex",color=ifelse(row_max[,'SEBA'],"blue","black"))) %>%
  #mutate(`TLO$^A$`=cell_spec(`TLO$^A$`,"latex",color=ifelse(row_max[,'TLO_A'],"blue","black"))) %>%
  mutate(Environment=linebreak(Environment)) %>%
  kable(
      #%>% order_by(c(EnvironmentClass,EnvironmentDimChange,EnvironmentValueChange))
      booktabs=T,format="latex"
      #,digits=2
      ,format.args=list(scientific=FALSE)
      ,escape=F
      ,align="lrlrrrrr"
      ) %>%
  column_spec(1,width="5em") %>%
  column_spec(2,width="4em") %>%
  column_spec(3,width="4.5em") %>%
   collapse_rows(valign="top",latex_hline="custom",custom_latex_hline=1:2) %>%
  #pander(split.cell=10,split.table=Inf)
  writeLines("../../../output/tables/table_2_main_significance.tex")
```



## Average online performance as line graphs

```{r}
print(paste0("number of experiment runs in this dataset: ",max(run_summary$RunId)))
```



```{r fig.width=8, fig.height=7}



# activity_means <- data.table(raw_activity)[EpisodeType=="Online"] %>% 
#   select(`R^*`,Agent,Environment,EnvironmentClass,EnvironmentVariant,ObjectiveDimChange,EnvironmentValueChange) %>%
#   group_by(EnvironmentClass, Environment, Agent,EnvironmentVariant,ObjectiveDimChange,EnvironmentValueChange) %>% summarise_all(mean) %>% data.table
activity_means <- run_summary[
  EpisodeType=="Online" & # Agent!="Linear"
  Agent %in% c("SEBA2", "SFLLA2","TLO_A","LIN_SUM")
  ]

#activity_means %>% group_by(Agent,EnvironmentValueChange, ObjectiveDimChange, EnvironmentClass) %>% summarise(rowCount = length(`R^*`))
#activity_means %>% group_by(Agent,EnvironmentValueChange, ObjectiveDimChange, EnvironmentClass) %>% summarise(rowCount = length(`R^*`)) %>% .$rowCount %>% table
activity_means <- activity_means %>% group_by(Agent,EnvironmentValueChange, ObjectiveDimChange) %>% 
  mutate(
    Bottom5Pc = quantile(`R^*`,0.05),
    Top5Pc = quantile(`R^*`,0.95)
    )

activity_means_trimmed <- activity_means %>% filter(`R^*`>Bottom5Pc & `R^*`<Top5Pc)


#now do 
for (env_dim in c("Performance","Alignment")){
    env_dim_descriptive <- env_dim
    if(env_dim=="Performance"){
      env_dim_descriptive<-"Primary"
    }
  relevant_activity <- activity_means_trimmed %>% dplyr::filter(ObjectiveDimChange %in% c("",env_dim)) %>% use_display_names
  

    baseplot <- ggplot(relevant_activity,aes(x=EnvironmentValueChange,y=`R^*`,fill=Agent,color=Agent,group=interaction(Agent,EnvironmentValueChange)))+
      #geom_point(size=6,alpha=0.4,shape=21,color="black")+
      #geom_violin(position="identity",alpha=0.2,size=0.1)+
      geom_violin(position="dodge",alpha=0.2,size=0.1)+
      scale_x_continuous(trans="log10",
                         limits = c(min(relevant_activity$EnvironmentValueChange)/5,max(relevant_activity$EnvironmentValueChange)*10),
                         breaks = c(0.01,0.1,1,10,100))+
      #coord_cartesian(ylim=c(-40,20))+
      #geom_line(linetype="dashed")+
      geom_dl(aes(label=Agent),method=list("last.qp",cex=0.7),alpha=1,position=position_nudge(x=500))+
      
      facet_wrap(~EnvironmentClass,scales = "free_y")+theme(axis.text.x = element_text(angle=30),legend.position = "bottom")+
        labs(
          x=paste0(env_dim, " Scale"),
          
          title=paste0(env_dim, " Scaling: Average Online Performance"),subtitle=paste("Mean across all 5000 episodes over middle 90% of experiment repetitions"))
      
    paper_plot <- baseplot 

    ggsave(filename=paste0(output_dir, comparison_folder, "online_util_transform_",env_dim,".pdf"),plot=paper_plot,device="pdf",width = 6,height=7)
    
    presentation_plot <- baseplot
            
    
    # ggsave(filename=paste0(output_dir, "online",env_dim,".png"),plot=presentation_plot,device="png",width = 6,height=6)
    
    print(presentation_plot)
}


```
localchange
```{r eval=FALSE, include=FALSE}
relevant_activity <- activity_means %>% dplyr::filter(ObjectiveDimChange %in% c("",env_dim) & (EnvironmentClass=="Sokoban") & EnvironmentValueChange==1
                                                      & Agent=="SFLLA"
                                                      )
    baseplot <- ggplot(relevant_activity,aes(x=`R^*`,fill=Agent,color=Agent,group=Agent))+
      geom_histogram()
    
    
  #baseplot
```


## Average online performance for TLO_A vs. SFLLA, all metrics, BreakableBottles

```{r eval=FALSE, fig.width=8, include=FALSE}

activity_means <- run_summary[EpisodeType=="Online" & (Agent %in% c("TLO_A","SFLLA")) & (EnvironmentClass=="BreakableBottles")] %>%
  select(`R^*`,`R^P`,`R^A`,Agent,Environment,EnvironmentClass,EnvironmentVariant,ObjectiveDimChange,EnvironmentValueChange) %>%
  melt(measure.vars = c("R^*","R^P","R^A"))
  

#now do 
for (ec in unique(activity_means$EnvironmentClass)){
  for (env_dim in c("Performance","Alignment")){
    env_dim_descriptive <- env_dim
    if(env_dim=="Performance"){
      env_dim_descriptive<-"Primary"
    }
    relevant_activity <- activity_means %>% dplyr::filter((ObjectiveDimChange %in% c("",env_dim)) & EnvironmentClass==ec)
      baseplot <- ggplot(relevant_activity,aes(x=EnvironmentValueChange,y=value,fill=Agent,color=Agent,group=interaction(Agent,EnvironmentValueChange)))+
        #geom_point(size=6,alpha=0.4,shape=21,color="black")+
        geom_violin(position="identity",alpha=0.4,size=1.5)+
        scale_x_continuous(trans="log10",
                           limits = c(min(relevant_activity$EnvironmentValueChange),max(relevant_activity$EnvironmentValueChange)*10),
                           breaks = c(0.01,0.1,1,10,100))+
        #geom_line(linetype="dashed")+
        geom_dl(aes(label=Agent),method=list("last.qp",cex=0.7),alpha=1,position=position_nudge(x=500))+
        facet_wrap(~variable,scales = "free_y")+theme(axis.text.x = element_text(angle=30),legend.position = "bottom")+
          labs(
            x=paste0(env_dim, " objective reward transform magnitude"),
            
            title=paste0(env_dim, paste0(" Objective Transformation: Average Online Score for ",ec)),
            subtitle="Across 5000 trials"
            )
        
      paper_plot <- baseplot 
      #ggsave(filename=paste0(output_dir, "online",env_dim,".pdf"),plot=paper_plot,device="pdf",width = 6,height=7)
      presentation_plot <- baseplot
      #ggsave(filename=paste0(output_dir, "online",env_dim,".png"),plot=presentation_plot,device="png",width = 6,height=6)
      print(presentation_plot)
      

  }
  
}


```


### Time graphs


```{r}


get_blackman_smoothing_function <- function(smoothing_level){
  blackman_x_window <- signal::blackman(smoothing_level)/sum(signal::blackman(smoothing_level))
  smoothing_function <- function(steps){
    return(sum(blackman_x_window*steps))
  }
  return(smoothing_function)
}

blackman10_function<-get_blackman_smoothing_function(10)
blackman20_function<-get_blackman_smoothing_function(20)
blackman50_function<-get_blackman_smoothing_function(50)
blackman200_function<-get_blackman_smoothing_function(200)

```


```{r}
episode_summary_long <-melt.data.table(
  episode_summary[,setdiff(colnames(episode_summary),c("EnvironmentVariant","EnvironmentDimChange")),with=FALSE],
  id.vars =c("EpisodeType","Episode number","Agent","Environment","EnvironmentClass",
             "EnvironmentValueChange","ObjectiveDimChange"),
  variable.name = "Measure",value.name="Score")

episode_summary_long[is.na(EnvironmentValueChange),EnvironmentValueChange:=1]
#activity_long %>% group_by(Measure,EpisodeType,Agent,Environment,RunId)

episode_summary_long[,Score_BMS_10:=frollapply(Score,10,blackman10_function),.(Measure,EpisodeType,Agent,Environment,EnvironmentClass,EnvironmentValueChange,ObjectiveDimChange)]

episode_summary_long[,Score_BMS_50:=frollapply(Score,50,blackman50_function),.(Measure,EpisodeType,Agent,Environment,EnvironmentClass,EnvironmentValueChange,ObjectiveDimChange)]

```


```{r fig.width=8}
# 
# time_graph_data <- episode_summary_long[EnvironmentValueChange==1 & Measure=="R^*"]
# #R* over agents, base scaling.
# # for (select_dim in unique(episode_summary_long$ObjectiveDimChange)){
# #   time_graph_data_display <- episode_summary_long[ObjectiveDimChange==select_dim]
# #   
# # }
# # for (select_env in unique(time_graph_data$Environment)){
#   to_plot <- ggplot(
#   time_graph_data[EpisodeType=="Online"],
#   aes(x=`Episode number`,y=Score_BMS_50,color=Agent,group=Agent)
#   )+geom_line(alpha=0.5,size=1)+
#   theme(legend.position="bottom")+
#   coord_cartesian(xlim = c(0,max(time_graph_data$`Episode number`,na.rm = TRUE)*1.2))+
#   geom_dl(aes(label=Agent),method=list("last.qp",cex=1),alpha=1)+
#   labs(y="Score")+facet_wrap(~Environment,scales="free")
#   
# print(to_plot)
# # }
# 


```



```{r fig.width=10 }
# table(episode_summary_long$ObjectiveDimChange)
# 
# time_graph_data <- episode_summary_long[Measure=="R^*" & Agent!="Linear"]
# time_graph_data$Condition <- paste0(time_graph_data$ObjectiveDimChange,time_graph_data$EnvironmentValueChange)
# time_graph_data <- time_graph_data[(time_graph_data$`Episode number` %%50)==0,]
# #R* over agents, base scaling.
# # for (select_dim in unique(episode_summary_long$ObjectiveDimChange)){
# #   time_graph_data_display <- episode_summary_long[ObjectiveDimChange==select_dim]
# #   
# # }
#  for (select_env in unique(time_graph_data$EnvironmentClass)){
#   to_plot <- ggplot(
#   time_graph_data[EpisodeType=="Online" & EnvironmentClass==select_env],
#   aes(x=`Episode number`,y=Score_BMS_50,color=Agent,group=Agent)
#   )+geom_line(alpha=0.5,size=1)+
#   theme(legend.position="bottom")+facet_wrap(~Condition,scales="free")+
#   coord_cartesian(xlim = c(0,max(time_graph_data$`Episode number`,na.rm = TRUE)*1.2))+
#   geom_dl(aes(label=Agent),method=list("last.qp",cex=1),alpha=1)+
#   labs(y="Score",title=select_env)
#   
# print(to_plot)
#  }
# 


```

### Viewing R* and R^A for each environment



```{r }
table(episode_summary_long$ObjectiveDimChange)

tloa_sflla_compare <- episode_summary_long#[Agent %in% c("TLO_A","SFLLA","EEBA1","LIN_SUM")]
tloa_sflla_compare$Condition <- paste0(tloa_sflla_compare$ObjectiveDimChange,tloa_sflla_compare$EnvironmentValueChange)

#to speed up plotting, only plot every 10th episode or even every 100th
tloa_sflla_compare <- tloa_sflla_compare[(tloa_sflla_compare$`Episode number` %%10)==0,]

tloa_sflla_compare <- tloa_sflla_compare[tloa_sflla_compare$EnvironmentValueChange %in% c(0.01,1,100)]
```


```{r fig.width=12}
for (select_env in unique(tloa_sflla_compare$EnvironmentClass)){
  to_plot <- ggplot(
    tloa_sflla_compare[EpisodeType=="Online" & EnvironmentClass==select_env],
    aes(x=`Episode number`,y=Score_BMS_50,color=Agent,group=Agent)
    )+geom_line(alpha=0.5,size=1)+
    theme(legend.position="bottom")+facet_wrap(Measure~Condition,scales="free",ncol = 5)+
    coord_cartesian(xlim = c(0,max(tloa_sflla_compare$`Episode number`,na.rm = TRUE)*1.2))+
    geom_dl(aes(label=Agent),method=list("last.qp",cex=0.8),alpha=1)+
    labs(y="Score",title=select_env)
  
  print(to_plot)
  
  ggsave(filename=paste0(output_dir, comparison_folder, "_progress_",select_env,".pdf"),plot=to_plot,device="pdf",width = 12,height=10)
}



```


