---
title: "R Notebook"
output: html_notebook
---

This notebook demos opening different Excel files and printing their output.
```{r}
library(readxl)
library(data.table)
library(ggplot2)
library(dplyr)
library(signal)
library(stringr)
library(directlabels)

```


```{r}
TLO_A_sheetlist <- readxl::excel_sheets("../data/bjs_5000epi/BreakableBottles-TLO_A(SafetyFirstMO)-SOFTMAY_T10-alpha0.1-lambda0.95.xls")

stopifnot(TLO_A_sheetlist==c("Trial0","Summary","Collated"))

TLO_A_summary <- readxl::read_xls("../data/bjs_5000epi/BreakableBottles-TLO_A(SafetyFirstMO)-SOFTMAY_T10-alpha0.1-lambda0.95.xls",
                                  sheet = "Summary",skip = 1)
colnames(TLO_A_summary) <- c("TrialType","TrialNum", paste0(rep(c("R^P","R^A","R^*"),3),"_", rep(c("Average","Min","Max","Median"),each=3)))
```
Try it a different way....

```{r}
TLO_A_summary_index <- readxl::read_xls("../data/bjs_5000epi/BreakableBottles-TLO_A(SafetyFirstMO)-SOFTMAY_T10-alpha0.1-lambda0.95.xls",
                                  sheet = "Summary",range = "A2:B5003",skip = 1)

TLO_A_summary_median <- readxl::read_xls("../data/bjs_5000epi/BreakableBottles-TLO_A(SafetyFirstMO)-SOFTMAX_T10-alpha0.1-lambda0.95.xls",
                                  sheet = "Summary",range = "L2:N5003",skip = 1,col_types="text")

colnames(TLO_A_summary_index) <- c("TrialType","TrialNum")

cbind(TLO_A_summary_index,TLO_A_summary_median)
```

Read the first page...


```{r}

TLO_A_page0 <- data.table(readxl::read_xls("../data/bjs_5000epi/BreakableBottles-TLO_A(SafetyFirstMO)-SOFTMAY_T10-alpha0.1-lambda0.95.xls",
                                  sheet = "Trial0"))

colnames(TLO_A_page0)[1] <- "EpisodeType"

TLO_A_page0$`Episode number` <- as.numeric(TLO_A_page0$`Episode number`)
```

```{r}
TLO_A_page0_long <-melt(TLO_A_page0,id.vars =c("EpisodeType","Episode number"),variable.name = "Measure",value.name="Score")
blackman50_window <- signal::blackman(50)/sum(signal::blackman(50))

blackman50_function<-function(steps){
  return(sum(blackman50_window*steps))
}
TLO_A_page0_long <- TLO_A_page0_long %>% group_by(Measure,EpisodeType) %>% 
  mutate(
    ScoreRMean10 = frollmean(Score,20),
    ScoreBlackman = frollapply(Score,50,blackman50_function)
    ) %>% ungroup %>% data.table
```


```{r}


ggplot(TLO_A_page0_long[EpisodeType=="Online"],aes(x=`Episode number`,y=ScoreBlackman))+geom_line()+
  labs(y="Score")+facet_grid(cols = vars(Measure),scales="free_y")

```


Now--great--can we compare different sheets?

```{r}
#list files
files <- list.files("../data/bjs_5000epi/")
#regex read the main properties of each sheet
file_list <- stringr::str_match(files,'^(\\w*)-(\\w*)\\((\\w*)\\)') %>% data.frame %>% cbind(files,.)
colnames(file_list) <- c("filename","full_code","Environment","Agent","AgentClass")

#now we want to iterate through each of those and output the data
raw_activity_list <- apply(file_list,1,function(row){
 print(row[["full_code"]]) 
  #load the spreadsheet
  TLO_A_page0 <- readxl::read_xls(
    paste0("../data/bjs_5000epi/",row[["filename"]]),
    sheet = "Trial0")
  
  #clean the data
  colnames(TLO_A_page0)[1] <- "EpisodeType"
  TLO_A_page0$`Episode number` <- as.numeric(TLO_A_page0$`Episode number`)
  #label the data
  TLO_A_page0$Agent <- row[["Agent"]]
  TLO_A_page0$Environment <- row[["Environment"]]
  return(TLO_A_page0)
})

raw_activity <- do.call(rbind,raw_activity_list)
print(object.size(raw_activity))
#get memory efficiencies
raw_activity$EpisodeType <- as.factor(raw_activity$EpisodeType)
raw_activity$Environment <- as.factor(raw_activity$Environment)
raw_activity$Agent <- as.factor(raw_activity$Agent)
print(object.size(raw_activity))


```


Now we apply some of the postprocessing we did before:


```{r}
activity_long <-melt.data.table(data.table(raw_activity),id.vars =c("EpisodeType","Episode number","Agent","Environment"),variable.name = "Measure",value.name="Score")
blackman50_window <- signal::blackman(50)/sum(signal::blackman(50))

blackman50_function<-function(steps){
  return(sum(blackman50_window*steps))
}
activity_long <- activity_long %>% group_by(Measure,EpisodeType,Agent,Environment) %>% 
  mutate(
    ScoreRMean10 = frollmean(Score,20),
    ScoreBlackman = frollapply(Score,50,blackman50_function)
    ) %>% ungroup %>% data.table

print(object.size(activity_long))

```

```{r fig.width=14}


ggplot(
  activity_long[EpisodeType=="Online" & Environment=="BreakableBottles" ],
  aes(x=`Episode number`,y=ScoreBlackman,color=Agent,group=Agent)
  )+geom_line(alpha=0.5,size=1)+
  theme(legend.position="bottom")+
  geom_dl(aes(label=Agent),method= "last.qp",alpha=1)+
  labs(y="Score")+facet_grid(cols = vars(Measure),scales="free_y")


```
Eliminate the worst two to make this a bit easier to read....


```{r fig.width=14}

for (model_env in unique(activity_long$Environment)){
  myplot <- ggplot(
  activity_long[EpisodeType=="Online" & Environment==model_env & !(Agent %in% c("ELA","MIN","SingleObjective")) ],
  aes(x=`Episode number`,y=ScoreBlackman,color=Agent,group=Agent)
  )+geom_line(alpha=0.5,size=1)+
  theme(legend.position="bottom")+
  coord_cartesian(xlim=c(0,5500))+
  geom_dl(aes(label=Agent),method= list("last.bumpup", cex = 0.5))+
  labs(y="Score",title=model_env)+#facet_grid(cols = vars(Measure),scales="free")
  facet_wrap(Measure~.,nrow=1,scales="free")

print(myplot)
}

```



I think the absolute best we can hope for is to reach performance equivalent to the Linear environment for the $R^P$ but equivalent to the overall level in $R^*$. The Sokoban environment most clearly shows those differences.

## Offline performance

```{r}
for(model_env in unique(raw_activity$Environment)){
  table_env <- data.table(raw_activity)[EpisodeType=="Offline" & Environment==model_env,]
  table_env$EpisodeType=NULL
  print(knitr::kable(table_env))
  
}


```







