---
title: "R Notebook"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

This notebook demos opening different Excel files and printing their output.
```{r}
library(readxl)
library(data.table)
library(ggplot2)
library(signal)

library(dplyr)
library(stringr)
library(directlabels)

source("utils.R")
output_dir <- "../../../output/"
```

Now--great--can we compare different sheets?

```{r message=FALSE}
source_path <- "../data/comparison_4envs//"

file_list <- get_file_list(source_path)

raw_activity <- get_raw_activity(file_list,source_path)

print(object.size(raw_activity))
#get memory efficiencies
raw_activity$EpisodeType <- as.factor(raw_activity$EpisodeType)
raw_activity$Environment <- as.factor(raw_activity$Environment)
raw_activity$Agent <- as.factor(raw_activity$Agent)
print(object.size(raw_activity))


```


Filter out SFMLA because it hasn't performed well and there's no point including it.

```{r}
raw_activity <- raw_activity[raw_activity$Agent!="SFMLA",]
```



Now we apply some of the postprocessing we did before:


```{r}
activity_long <-melt.data.table(data.table(raw_activity),id.vars =c("EpisodeType","Episode number","Agent","Environment","EnvironmentClass"),variable.name = "Measure",value.name="Score")


activity_long <- append_blackman_averaging(activity_long)

print(object.size(activity_long))

```

## Offline performance





```{r}
table_env <- data.table(raw_activity)[EpisodeType=="Offline",]
table_env$EpisodeType=NULL
#table_env$Environment=NULL
table_env$`Episode number`=NULL

```

Maybe we want a table with just R*. Then we can put agent along one axis and environment along the other.



```{r}
table_env <- data.table(raw_activity)[EpisodeType=="Offline",]
table_env$EpisodeType=NULL
#table_env$Environment=NULL
table_env$`Episode number`=NULL
table_env$`R^P`=NULL
table_env$`R^A`=NULL

table_env_long <- table_env %>% dcast.data.table(Environment~Agent,value.var="R^*",fun.aggregate = mean)
print(knitr::kable(table_env_long))


```

## Additional data labelling

```{r}

environment_labels <- str_match(raw_activity$Environment,"(pen|rew)(\\d+.?\\d*)")
raw_activity$EnvironmentVariant <- environment_labels[,1]
raw_activity$EnvironmentDimChange <- environment_labels[,2]
raw_activity$EnvironmentValueChange <- as.numeric(environment_labels[,3])
raw_activity[is.na(raw_activity$EnvironmentVariant),]$EnvironmentVariant <- "Base"
raw_activity[is.na(raw_activity$EnvironmentDimChange),]$EnvironmentDimChange <- ""
raw_activity[is.na(raw_activity$EnvironmentValueChange),]$EnvironmentValueChange <- 1
```


## Offline performance

```{r}

activity_means <- data.table(raw_activity)[EpisodeType=="Offline"] %>% 
  select(`R^*`,Agent,Environment,EnvironmentClass) %>%
  group_by(EnvironmentClass, Environment, Agent) %>% summarise_all(mean) %>% data.table

#table_env_long <- activity_means %>% data.table %>% dcast.data.table(Environment~Agent,value.var="R^*")
#print(knitr::kable(table_env_long))

#now do 

for(envclass in unique(activity_means$EnvironmentClass)){
  envplot <- ggplot(activity_means[EnvironmentClass==envclass,],aes(x=Environment,y=`R^*`,fill=Agent))+geom_bar(stat="identity",position="dodge")+
  #geom_line(data=activity_means[activity_means$Agent=='TLO_A',],mapping = aes(x=Environment,y=`R^*`,group=Agent),linetype="dashed")+
  theme(axis.text.x = element_text(angle=30))+
    labs(title=envclass)
  
  print(envplot)
}


```


## Average online performance

```{r}

activity_means <- data.table(raw_activity)[EpisodeType=="Online"] %>% 
  select(`R^*`,Agent,Environment,EnvironmentClass,EnvironmentVariant) %>%
  group_by(EnvironmentClass, Environment, Agent,EnvironmentVariant) %>% summarise_all(mean) %>% data.table

#table_env_long <- activity_means %>% data.table %>% dcast.data.table(Environment~Agent,value.var="R^*")
#print(knitr::kable(table_env_long))

#now do 

for(envclass in unique(activity_means$EnvironmentClass)){
  envplot <- ggplot(activity_means[EnvironmentClass==envclass,],aes(x=EnvironmentVariant,y=`R^*`,fill=Agent))+geom_bar(stat="identity",position="dodge")+
  #geom_line(data=activity_means[activity_means$Agent=='TLO_A',],mapping = aes(x=Environment,y=`R^*`,group=Agent),linetype="dashed")+
  theme(axis.text.x = element_text(angle=30))+
    labs(title=paste0(envclass, ": Average Online Performance"),subtitle="Across 5000 trials")
  
  print(envplot)
}


```


## Average online performance as line graphs

```{r fig.width=12}

activity_means <- data.table(raw_activity)[EpisodeType=="Online"] %>% 
  select(`R^*`,Agent,Environment,EnvironmentClass,EnvironmentVariant,EnvironmentDimChange,EnvironmentValueChange) %>%
  group_by(EnvironmentClass, Environment, Agent,EnvironmentVariant,EnvironmentDimChange,EnvironmentValueChange) %>% summarise_all(mean) %>% data.table


#now do 
for (env_dim in c("pen","rew")){
  relevant_activity <- activity_means %>% dplyr::filter(EnvironmentDimChange %in% c("",env_dim))
    envplot <- ggplot(relevant_activity,aes(x=EnvironmentValueChange,y=`R^*`,fill=Agent,color=Agent))+
      geom_point(size=6,alpha=0.4,shape=21,color="black")+
      scale_x_continuous(trans="log10",
                         limits = c(min(relevant_activity$EnvironmentValueChange),max(relevant_activity$EnvironmentValueChange)*10),
                         breaks = c(0.01,0.1,1,10,100))+
      geom_line(linetype="dashed")+
      geom_dl(aes(label=Agent),method=list("last.qp",cex=0.7),alpha=1)+
      facet_wrap(~EnvironmentClass,scales = "free_y")+
      theme(axis.text.x = element_text(angle=30))+
        labs(
          x=paste0(env_dim, " Scale"),
          title=paste0("Average Online Performance across different ", env_dim, " scale levels"),subtitle="Across 5000 trials")
      
    print(envplot)
}


```


## Average offline performance as line graphs

```{r fig.width=12}

activity_means <- data.table(raw_activity)[EpisodeType=="Offline"] %>% 
  select(`R^*`,Agent,Environment,EnvironmentClass,EnvironmentVariant,EnvironmentDimChange,EnvironmentValueChange) %>%
  group_by(EnvironmentClass, Environment, Agent,EnvironmentVariant,EnvironmentDimChange,EnvironmentValueChange) %>% summarise_all(mean) %>% data.table


#now do 
for (env_dim in c("pen","rew")){
  relevant_activity <- activity_means %>% dplyr::filter(EnvironmentDimChange %in% c("",env_dim))
    envplot <- ggplot(relevant_activity,aes(x=EnvironmentValueChange,y=`R^*`,fill=Agent,color=Agent))+
      geom_point(size=6,alpha=0.4,shape=21,color="black")+
      scale_x_continuous(trans="log10",
                         limits = c(min(relevant_activity$EnvironmentValueChange),max(relevant_activity$EnvironmentValueChange)*10),
                         breaks = c(0.01,0.1,1,10,100))+
      geom_line(linetype="dashed")+
      geom_dl(aes(label=Agent),method=list("last.qp",cex=0.7),alpha=1)+
      facet_wrap(~EnvironmentClass,scales = "free_y")+
      theme(axis.text.x = element_text(angle=30))+
        labs(
          x=paste0(env_dim, " Scale"),
          title=paste0("Average Offline Performance across different ", env_dim, " scale levels"),subtitle="Across 5000 trials")
    ggsave(filename=paste0(output_dir, "offline performance_",env_dim,".eps"),plot=envplot,device="eps")
    ggsave(filename=paste0(output_dir, "offline performance_",env_dim,".tex"),plot=envplot,device="tex")
    ggsave(filename=paste0(output_dir, "offline performance_",env_dim,".pdf"),plot=envplot,device="pdf")
    ggsave(filename=paste0(output_dir, "offline performance_",env_dim,".png"),plot=envplot,device="png")
    print(envplot)
}


```

### Individual graphs



```{r fig.width=14}

for (select_env in unique(activity_long$Environment)){
  to_plot <- ggplot(
  activity_long[EpisodeType=="Online" & Environment==select_env ],
  aes(x=`Episode number`,y=ScoreBlackman200,color=Agent,group=Agent)
  )+geom_line(alpha=0.5,size=1)+
  theme(legend.position="bottom")+
  coord_cartesian(xlim = c(0,max(activity_long$`Episode number`,na.rm = TRUE)*1.2))+
  geom_dl(aes(label=Agent),method=list("last.qp",cex=1),alpha=1)+
  labs(y="Score",title=select_env)+facet_wrap(~Measure,scales="free")
  print(to_plot)
}



```

