---
title: "R Notebook"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

This notebook demos opening different Excel files and printing their output.
```{r}
library(readxl)
library(data.table)
library(ggplot2)
library(dplyr)
library(signal)
library(stringr)
library(directlabels)

```


Now--great--can we compare different sheets?




```{r}
#list files
source_path <- "../data/test_with_rolands_new_code/"
files <- list.files(source_path)
#regex read the main properties of each sheet
file_list <- stringr::str_match(files,'^(\\w*)-(\\w*)\\((\\w*)\\)') %>% data.frame %>% cbind(files,.)
colnames(file_list) <- c("filename","full_code","Environment","Agent","AgentClass")

#now we want to iterate through each of those and output the data
raw_activity_list <- apply(file_list,1,function(row){
 print(row[["full_code"]]) 
  #load the spreadsheet
  TLO_A_page0 <- readxl::read_xls(
    paste0(source_path,row[["filename"]]),
    sheet = "Trial0")
  
  #clean the data
  colnames(TLO_A_page0)[1] <- "EpisodeType"
  TLO_A_page0$`Episode number` <- as.numeric(TLO_A_page0$`Episode number`)
  #label the data
  TLO_A_page0$Agent <- row[["Agent"]]
  TLO_A_page0$Environment <- row[["Environment"]]
  return(TLO_A_page0)
})

raw_activity <- do.call(rbind,raw_activity_list)
print(object.size(raw_activity))
#get memory efficiencies
raw_activity$EpisodeType <- as.factor(raw_activity$EpisodeType)
raw_activity$Environment <- as.factor(raw_activity$Environment)
raw_activity$Agent <- as.factor(raw_activity$Agent)
print(object.size(raw_activity))


```


Now we apply some of the postprocessing we did before:


```{r}
activity_long <-melt.data.table(data.table(raw_activity),id.vars =c("EpisodeType","Episode number","Agent","Environment"),variable.name = "Measure",value.name="Score")
blackman50_window <- signal::blackman(50)/sum(signal::blackman(50))

blackman50_function<-function(steps){
  return(sum(blackman50_window*steps))
}
blackman200_window <- signal::blackman(200)/sum(signal::blackman(200))
blackman200_function<-function(steps){
  return(sum(blackman200_window*steps))
}
activity_long <- activity_long %>% group_by(Measure,EpisodeType,Agent,Environment) %>% 
  mutate(
    ScoreRMean10 = frollmean(Score,20),
    ScoreBlackman = frollapply(Score,50,blackman50_function),
    ScoreBlackman200 = frollapply(Score,200,blackman200_function)
    ) %>% ungroup %>% data.table

print(object.size(activity_long))

```

```{r fig.width=14}


ggplot(
  activity_long[EpisodeType=="Online" & Environment=="BreakableBottles" ],
  aes(x=`Episode number`,y=ScoreBlackman200,color=Agent,group=Agent)
  )+geom_line(alpha=0.5,size=1)+
  theme(legend.position="bottom")+
  geom_dl(aes(label=Agent),method= "last.qp",alpha=1)+
  labs(y="Score")+facet_wrap(~Measure,scales="free")


```
Eliminate the worst two to make this a bit easier to read....


```{r fig.width=14}

for (model_env in unique(activity_long$Environment)){
  myplot <- ggplot(
  activity_long[EpisodeType=="Online" & Environment==model_env & !(Agent %in% c("ELA","MIN","SingleObjective")) ],
  aes(x=`Episode number`,y=ScoreBlackman200,color=Agent,group=Agent)
  )+geom_line(alpha=0.5,size=1)+
  theme(legend.position="bottom")+
  coord_cartesian(xlim=c(0,5500))+
  geom_dl(aes(label=Agent),method= list("last.bumpup", cex = 0.5))+
  labs(y="Score",title=model_env)+#facet_grid(cols = vars(Measure),scales="free")
  facet_wrap(Measure~.,nrow=1,scales="free")

print(myplot)
}

```


```{r fig.width=14}

for (model_env in unique(activity_long$Environment)){
  myplot <- ggplot(
  activity_long[EpisodeType=="Online" & Environment==model_env & !(Agent %in% c("ELA","MIN","SingleObjective")) 
                &(`Episode number` >=4000)
                ],
  aes(x=`Episode number`,y=ScoreBlackman200,color=Agent,group=Agent)
  )+geom_line(alpha=0.5,size=1)+
  theme(legend.position="bottom")+
  coord_cartesian(xlim=c(4000,5500))+
  geom_dl(aes(label=Agent),method= list("last.bumpup", cex = 0.5))+
  labs(y="Score",title=model_env)+#facet_grid(cols = vars(Measure),scales="free")
  facet_wrap(Measure~.,nrow=1,scales="free")

print(myplot)
}

```


I think the absolute best we can hope for is to reach performance equivalent to the Linear environment for the $R^P$ but equivalent to the overall level in $R^*$. The Sokoban environment most clearly shows those differences.


## Let's look at 

## Offline performance

```{r}
for(model_env in unique(raw_activity$Environment)){

  table_env <- data.table(raw_activity)[EpisodeType=="Offline" & Environment==model_env,]
  table_env$EpisodeType=NULL
  table_env$Environment=NULL
  table_env$`Episode number`=NULL
  print(model_env)
  print(knitr::kable(table_env,caption = model_env))
  
}


```



## Now what?

 - We can write a function to equalize the variance of each objective's input. We were always planning to do this. But I don't have a particular reason to think that'll help.
 - Come up with a better algorithm??? 
    - Not sure any conservative function can get us primary reward faster, though. It is designed to avoid that.
    - We might be able to come up with an algorithm that obtains the safety objective faster?
 - Think about other contexts where our approach would be more advantageous and see if we can implement _that_ environment.
 - 
 
 
 
 



